\LARGE \bf Approximately Orchestrated Road Traffic Automata:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-15 papers/itsc_2012/final.tex

OSM data has been used by traffic simulators in the past. MATSim is one such
multiagent simulator that focuses on performing large-scale simulations in a
relatively small amount of time \cite{balmer2009matsim}. Traffic demand is
supplied to MATSim in the form of \textit{plans} that an individual may intend
to follow in a given day. MATSim aims to iteratively improve these plans though
offline computation to maximize traffic throughput. In other words, it helps
individuals understand the best way to go about their daily routine to minimize
time spent in transit. This goal is somewhat different from that of AORTA,
where the demand supplied by individuals is taken as is. Rather than simply
improving routes, AORTA allows creating entirely different behaviors for both
vehicles and intersections.

Another popular open source traffic simulator that can use OSM data is SUMO
\cite{SUMO2011}, which shares the similar goals as AORTA. SUMO has been used to
study the effect of automated transportation systems, route planning of
individual vehicles, as well as dynamically adapting traffic signal policies to
increase traffic efficiency.  AORTA and SUMO differ in the manner in which
intersections are handled. SUMO uses traditional traffic signals, while AORTA
adopts a much more general \textit{reservation} system. A reservation tells a
car when it is safe to take its desired path through the intersection.
Reservations can be allotted to vehicles through more traditional means such as
traffic signals or stop-sign based intersection precedence, or through more
efficient methods designed specifically for autonomous vehicles
\cite{JAIR08-dresner}.
\commentd{Again, ``reservation'' feels like an overloaded term here, meaning the
general notion of being able to cross, as opposed to the specific policy.}

@@

\begin{figure}[h]
  \centering \includegraphics[width=\linewidth]{avg_lag_agent_atx.png}
  \caption{The distribution of average delay reveals that traffic signals can
           cause the most lag.}
  \label{fig:avg_lag}
  \vspace{-10pt}
\end{figure}
\commentc{This figure only shows the distributions for a particular
  traffic level only. People would wonder what is the traffic level.
Actually people are more interested to see how it varies with
different traffic levels so a few more graphs like this at
different traffic level is helpful.}
\commentc{Remove ``In this range'' in the y-label.}
\commentc{Replace ``lag'' with ``delay'' in the x-label}}

>>>>

OSM data has been used by traffic simulators in the past. MATSim is one such
multiagent simulator that focuses on performing large-scale simulations in a
relatively small amount of time \cite{balmer2009matsim}. Traffic demand is
supplied to MATSim in the form of \textit{plans} that an individual may intend
to follow in a given day. MATSim aims to iteratively improve these plans to
minimize traffic delays while minimizing the total amount of time by which agents
are late to their destinations. This goal is somewhat different from that of AORTA,
where the routes (demand) supplied by individuals is taken as is and does not have
a pre-determined ideal time of arrival. Rather than improving agent routes, AORTA
allows creating entirely different behaviors for both vehicles and intersections
in order to simulate a different environment instead of optimizing plans for a
society in a static environment.

Another popular open source traffic simulator that can use OSM data is SUMO
\cite{SUMO2011}, which shares many similar goals with AORTA. SUMO has been used to
study the effect of automated transportation systems, route planning of
individual vehicles, as well as dynamically adapting traffic signal policies to
increase traffic efficiency.  AORTA and SUMO differ in the manner in which
intersections are handled. SUMO uses traditional traffic signals, while AORTA
adopts a much more general \textit{reservation} system. A reservation tells a
car when it is safe to take its desired path through the intersection.
Reservations can be allotted to vehicles through more traditional means such as
traffic signals or stop-sign based intersection precedence, or through more
efficient methods designed specifically for autonomous vehicles
\cite{JAIR08-dresner}.
\commentm{Given that SUMO is also open-source and seems to be used fairly commonly
in the traffic community, our only real advantage over it is actually our choice
of language.  AORTA is much easier to use and extend primarily because we use
a higher level language.  (As we mention, our intersections are also more general,
but I think that's actually less important.)  I'm not sure of how to handle this.}
\commentd{Again, ``reservation'' feels like an overloaded term here, meaning the
general notion of being able to cross, as opposed to the specific policy.}

@@

\begin{figure}[h]
  \centering \includegraphics[width=\linewidth]{avg_lag_agent_atx.png}
  \caption{The distribution of average delay reveals that traffic signals can
           cause the most lag.}
  \label{fig:avg_lag}
  \vspace{-10pt}
\end{figure}
\commentc{This figure only shows the distributions for a particular
  traffic level only. People would wonder what is the traffic level.
Actually people are more interested to see how it varies with
different traffic levels so a few more graphs like this at
different traffic level is helpful.}
\commentc{Remove ``In this range'' in the y-label.}
\commentc{Replace ``lag'' with ``delay'' in the x-label}
